Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-03-01 src/tex/ms.tex
Will comments on 190521.

% Case: GW190521 (massive BBH)
\subsubsection{GW190521}
Even with the frequency-dependent birefringence model, some events still have a bimodal $\kappa$ distribution.
Consider GW190521, the most massive binary black hole merger in the events we included.
The degeneracy between $\kappa$ and $\iota$ cannot be broken by the frequency-dependent birefringence model, as shown in Fig.~\ref{fig:corner_GW190521}.
The reason could be this GW event's frequency range is too narrow to break the degeneracy.
The effect of birefringence at different frequencies within the range is similar, so the degeneracy cannot be broken.
Therefore, the narrow frequency range can be a possible reason why the $\kappa$ distribution of GW190521 is bimodal.
Note that $\kappa=0$ is still within the $90\%$ confidence interval, with a non-negligible probability.
The bimodal $\kappa$ distribution only means that the degeneracy between $\kappa$ and $\iota$ cannot be broken in this case.

@@

>>>>

% Case: GW190521 (massive BBH)
\subsubsection{GW190521}
Even with the frequency-dependent birefringence model, some events still have a bimodal $\kappa$ distribution.
Consider GW190521, the most massive binary black hole merger in the events we included.
The degeneracy between $\kappa$ and $\iota$ cannot be broken by the frequency-dependent birefringence model, as shown in Fig.~\ref{fig:corner_GW190521}.
The reason could be this GW event's frequency range is too narrow to break the degeneracy.
The effect of birefringence at different frequencies within the range is similar, so the degeneracy cannot be broken.
Therefore, the narrow frequency range can be a possible reason why the $\kappa$ distribution of GW190521 is bimodal.
Note that $\kappa=0$ is still within the $90\%$ confidence interval, with a non-negligible probability.
The bimodal $\kappa$ distribution only means that the degeneracy between $\kappa$ and $\iota$ cannot be broken in this case.  \wf{You should still explain \emph{why} the model seems to prefer $\left| \kappa \right| > 0$.  I \emph{think} the reason here is the distance prior---there is a lot more ``phase space'' at large distances that can be accessed by allowing $\kappa$ to be non-zero and choosing a corresponding inclination so that the amplification effects of birefringence are compensated for by the larger distance compared to the pure-GR run.  Does this make sense to you?  If so, can you write it up in this paragraph?}

@@

\section{GW170818}

\begin{figure}
    \script{corner_GW170818_appendix.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW170818_appendix.pdf}
    \caption{
        Corner plot of GW170818.
    }
    \label{fig:corner_GW170818_appendix}
\end{figure}
